% Compile with XeTeX

%{\LARGE\sffamily Scott Meisburger}

%{\sffamily 571 Prospect Ave. | Brooklyn, NY 11215 | 408.836.4502 | smeisburger@gmail.com}
\font\orator = "Orator Std Medium" at 11 pt
\font\oratorbig = "Orator Std Medium" at 22 pt
\font\oratorsmall = "Orator Std Medium" at 8 pt
\font\oratorslanted = "Orator Std Slanted" at 11 pt
\font\seriffont = "Georgia:mapping=tex-text" at 8 pt
\font\serifbold = "Georgia/B:mapping=tex-text" at 8 pt
\font\serifgreen = "Georgia:color=33AA88,mapping=tex-text" at 7 pt

\hoffset = - .5 in
\voffset = - .5 in
\vsize = 9 in

\parindent = 0 pt
\baselineskip = 12 pt

\def\scmtitle#1{\vskip 14 pt \leftline{\oratorslanted \uppercase{#1}} \vskip 6 pt}
\def\scmitem#1{\leftline{\hskip 10pt #1}}

\nopagenumbers

\seriffont

{\oratorbig \uppercase{S\kern -.180em c\kern -.200em o\kern -.230em t\kern -.250em t\kern -.220em \ M\kern -.170em e\kern -.210em i\kern -.260em s\kern -.200em b\kern -.130em u\kern -.180em r\kern -.140em g\kern -.200em e\kern -.220em r}}

\vskip 4.4 pt
\leftline{\oratorsmall 571 Prospect Ave.~| Brooklyn, NY 11215 | 408.836.4502 | smeisburger@gmail.com}

%% \scmtitle{Qualifications}
%% \scmitem{Open source technology expertise}
%% \scmitem{4 yrs.\ Python backend web experience}
%% \scmitem{iOS development experience}
%% \scmitem{Multi-disciplinary}

%% \scmitem{Languages+Libraries: Python, Flask, Django, Objective-C, JavaScript, HTML 5/CSS3}
%% %% \item{} Skills: version control, TDD, Dev-Ops, deployment, APIs
%% \scmitem{Tools: AWS, Emacs, Git, GNU/Linux, Mac OS X, Xcode}

\scmtitle{Professional Experience}

\halign{\hfil # \quad & # \hfil \cr
\serifgreen 2014--present & \serifbold Software Engineer at Alphaworks, a Betaworks Company \cr
& A Betaworks company. \cr
& \cr
\serifgreen 2012--present & \serifbold Senior Developer at Rhizome at the New Museum \cr
& Manages all aspects of Rhizome’s website and servers. \cr
& Technical advisor to the ArtBase, an award winning online archive of internet-based art. \cr
& \cr
\serifgreen 2011--2012 & \serifbold Software Engineer at Sanders New Media in Chicago, IL \cr
& Responsible for architecture, coding and deployment of iOS apps and Python web applications. \cr
& \cr
\serifgreen 2010--2011 & \serifbold Web Developer at Columbia College Chicago \cr
& Designed and developed student portfolio websites using HTML/CSS. \cr
& \cr
\serifgreen 2007--2010 & \serifbold Co-owner at Orchestral Colour Records in San Jose, CA \cr
& Co-founded independent record label in hometown promoting eclectic local artists. \cr
& \cr
\serifgreen Summer 2008 & \serifbold Volunteer at Computer History Museum in Mountain View, CA \cr
& Assisted with packaging and cataloging of computer related artifacts. \cr}

\scmtitle{Education}
\scmitem{Columbia College Chicago - BA in Photography, minor in Web Development, 2006 – 2010 cum laude.}
\scmitem{Foothill College - Various CS courses, Summers of ‘09 and ‘10.}

\scmtitle{Accolades}
\scmitem{Perspective Gallery - Work selected for LENSE 2011 juried exhibition.}
\scmitem{Poet and Didn’t Know it Award - The American Computer Experience 1998.}

\scmtitle{Shared Exhibitions}
\scmitem{2011 - Perspective Gallery, LENSE 2011.}
\scmitem{2011 - Photography B.A. + B.F.A. Manifest Exhibit.}

\scmtitle{Collections}
\scmitem{Columbia College Chicago Permanent Collection}

\scmtitle{Publications}
\scmitem{There and Back (Again): Homebrew Computer Club at 38. Rhizome Journal. December 16, 2013.}
\scmitem{http://rhizome.org/editorial/2013/dec/16/there-and-back-again-homebrew-computer-club-38/}

\bye
