% Compile with XeTeX

%% \font\sansbigred = "MyriadPro-Cond:color=CCCCCC" at 22 pt
\font\sans = "Letter Gothic Std:mapping=tex-text" at 7 pt
\font\sansbigger = "Letter Gothic Std:mapping=tex-text" at 8 pt
\font\sansbiggerbold = "Letter Gothic Std/B:mapping=tex-text" at 8 pt

\font\namefont = "Letter Gothic Std" at 25 pt
\font\sansbiggerbolditalic = "Letter Gothic Std/BI" at 8 pt

\nopagenumbers

\hoffset = - .5 in
\voffset = - .5 in
\hsize = 7.5 in
\vsize = 10 in

\baselineskip = 11 pt
\parindent = 0 pt
\sans

\def\scmtitle#1{\vskip 1.5\baselineskip \leftline{\sansbiggerbolditalic \uppercase{#1}} \vskip \baselineskip}
\def\scmitem#1{\leftline{- #1}}

\def\xpdate#1#2#3{\vtop{\baselineskip = .5\baselineskip \hsize .55 in
                                      \line{\hfil#1 \hfil}
                                      \line{\hfil #2 \hfil}
                                      \line{\hfil #3 \hfil}} \hskip .1 in}
\def\xpentry#1{\vtop{\hsize 2.75 in \tolerance 500 #1} \hskip .2 in}
\def\xprow#1#2{\line{#1 #2 \hfil} \vskip\baselineskip}
\def\xpsec#1#2#3#4{\xpdate{#1}{#2}{#3} \xpentry{#4}}

\def\xptitle#1#2{{\sansbiggerbold\uppercase{#1} }{\sansbigger . #2} \vskip .4\baselineskip}

\def\xpitem#1{\item{-}#1 \vskip .5\baselineskip}


{\namefont \uppercase{Scott Meisburger}}

\vskip .5\baselineskip
\leftline{\uppercase{New York City | 408.836.4502 | smeisburger@gmail.com | @protonpopsicle}}

\scmtitle{Overview}
\scmitem{Kowledgeable in the visual arts, design and aesthetics.}
\scmitem{Broad-ranging experience.}
\scmitem{A propensity for mastering technology tools and techniques.}

\scmtitle{Experience}

\xprow
{\xpsec{2014}{--}{present}{
        \xptitle{Alphaworks}{Software Engineer}
        \xpitem{Developed crowd-investing platform with experienced team at Betaworks.}
        \xpitem{Participated in code review.}
        \xpitem{Developed two generations of admin tools. \break(Flask, SQL-Alchemy)}
}}
{\xpsec{2012}{--}{present}{
        \xptitle{Rhizome}{Senior Developer}
        \xpitem{Principle architect and developer of rhizome.org, related microsites and special projects. (Google Glass, Raspberry Pi, D3.js).}
        %% \xpitem{by migrating physical infrastructure to AWS cloud, reducing costs by 86\%.}
        \xpitem{Opened up developement of site to community, released code under GPLv2.}
        \xpitem{Advises ArtBase, proof of concept work for para virtualized storage and retrieval of born-digital objects (Linux Containers, NGINX).}
}}

\xprow
{\xpsec{2011}{--}{2012}{
        \xptitle{Sanders New Media}{Software Engineer}
        \xpitem{Responsible for architecture, coding and deployment of iOS apps and Python web applications.}
}}
{\xpsec{2010}{--}{2011}{
        \xptitle{Columbia College Chicago}{Web Developer}
        \xpitem{Designed and developed student portfolio websites using HTML/CSS.}
}}

\xprow
{\xpsec{2007}{--}{2010}{
        \xptitle{Orchestral Colour Records}{Co-owner}
        \xpitem{Co-founded independent record label in hometown promoting eclectic local artists.}
}}
{\xpsec{Summer}{}{2008}{
        \xptitle{Computer History Museum}{Volunteer}
        \xpitem{Assisted with packaging and cataloging of computer related artifacts.}
}}

\scmtitle{Education}
\scmitem{Columbia College Chicago - BA in Photography, minor in Web Development, 2006 – 2010 cum laude.}
\scmitem{Foothill College - Various CS courses, Summers of ‘09 and ‘10.}

\scmtitle{Accolades}
\scmitem{Perspective Gallery - Work selected for LENSE 2011 juried exhibition.}
\scmitem{Poet and Didn’t Know it Award - The American Computer Experience 1998.}

\scmtitle{Shared Exhibitions}
\scmitem{2011 - Perspective Gallery, LENSE 2011.}
\scmitem{2011 - Photography B.A. + B.F.A. Manifest Exhibit.}

\scmtitle{Collections}
\scmitem{Columbia College Chicago Permanent Collection}

\scmtitle{Publications}
\scmitem{There and Back (Again): Homebrew Computer Club at 38. Rhizome Journal. December 16, 2013.}
\scmitem{http://rhizome.org/editorial/2013/dec/16/there-and-back-again-homebrew-computer-club-38/}

\bye
