% Compile with XeTeX

\font\sans = "Letter Gothic Std:mapping=tex-text" at 7 pt
\font\sansbigger = "Letter Gothic Std:mapping=tex-text" at 8 pt
\font\sansbiggerbold = "Letter Gothic Std/B:mapping=tex-text" at 8 pt
\font\sansbiggerbolditalic = "Letter Gothic Std/BI" at 8 pt
\font\namefont = "Letter Gothic Std" at 25 pt

\nopagenumbers

\hoffset = - .5 in
\voffset = - .5 in
\hsize = 7.5 in
\vsize = 10 in

\emergencystretch = 5 pt

\baselineskip = 11 pt
\parindent = 0 pt
\sans

\footline={\sans \TeX{} source available at https://github.com/protonpopsicle/resume/blob/master/MeisburgerS.tex \hfil Page \folio}

\def\title#1{\vskip 1.5\baselineskip \leftline{\sansbiggerbolditalic \uppercase{#1}} \vskip \baselineskip}
\def\bulpoint#1{\leftline{- #1}}

\def\date#1#2#3{\vtop{\baselineskip = .5\baselineskip \hsize .55 in
                                      \line{\hfil #1 \hfil}
                                      \line{\hfil #2 \hfil}
                                      \line{\hfil #3 \hfil}} \hskip .1 in}

\def\xprow#1#2{\line{#1 #2 \hfil} \vskip\baselineskip}
\def\xpcell#1#2#3#4{\date{#1}{#2}{#3} \xpbody{#4}}
\def\xpbody#1{\vtop{\hsize 2.75 in #1} \hskip .2 in}
\def\xptitle#1#2{{\sansbiggerbold\uppercase{#1} }{\sansbigger . #2} \vskip .4\baselineskip}
\def\xptitlelong#1#2{\leftline{\sansbiggerbold\uppercase{#1}} \leftline{\sansbigger #2} \vskip .4\baselineskip}
\def\xpbul#1{\item{-}#1 \vskip .5\baselineskip}


{\namefont \uppercase{Scott Meisburger}}

\vskip .5\baselineskip
\leftline{\uppercase{99 Gold St Apt 4C, Brooklyn NY | 408.836.4502 | smeisburger@gmail.com}}

\title{Overview}
\bulpoint{Highly skilled in leading technical teams.}
\bulpoint{Deep experience in open-source application development.}
\bulpoint{Proven experience building engineering organizations.}
\bulpoint{Expertise in people management, IoT, real-time web, multimedia and cloud infrastructure.}

\title{Experience}

\xprow
{\xpcell{2022}{--}{present}{
        \xptitlelong{AT\&T}{Director Technology-Product Development}
        \xpbul{Led software engineering initiatives in close collaboration with product, design and business teams resulting in successful launch of new products for AT\&T Business (SMS APIs, Developer Experience, Business portal transformation) opening new revenue channels and reducing time to market for new product offerings.}
        \xpbul{Nominated as calibrated hiring expert accountable for ensuring high-quality hiring decisions across multiple teams.}
        \xpbul{Implemented staffing plan to insource and rapidly transform mission-critical legacy applications and led end-to-end execution ensuring critical security improvements.}
        \xpbul{Mentored engineering leaders in 4 offices, provided coaching and hands-on technical oversight in full-stack development, DevOps and security.}
        \xpbul{Developed new engineering processes, drove adoption of industry best-practices and implemented new programs including peer tech demos to empower teams and foster strong engineering culture.}
}}
{\xpcell{2018}{--}{2022}{
        \xptitlelong{Samsung SmartThings}{Engineering Manager, AV Platform}
        \xpbul{Managed junior and senior level engineers, provided coaching and mentoring leading to career growth and development.}
        \xpbul{Led engineering efforts in close collaboration with Samsung mobile managers and engineers at HQ (Suwon, KOR).}
        \xpbul{Successfully delivered audio-video streaming services, allowing for Samsung home products (appliances, TVs, mobile devices) to connect and stream media to SmartThings clients.}
        \xpbul{Team drove architecture and standards for end-to-end encryption (privacy), P2P live streaming (reduced latency, cost) and AV cloud services.}
}}

\xprow
{\xpcell{2016}{--}{2018}{
        \xptitlelong{Samsung SmartThings}{Senior Software Engineer}
        \xpbul{Launched first-party SmartThings cameras. Worked with device manufacturers on firmware specs, over-the-air updates and security protocols.}
        \xpbul{Built major cloud services in Python: API server, media server and distributed messaging bus.}
        \xpbul{Supported global product rollout for strategic partnership between Samsung Mobile and wireless carriers.}
}}
{\xpcell{2014}{--}{2016}{
        \xptitlelong{Perch at Samsung Accelerator}{Software Engineer}
        \xpbul{Home monitoring startup. Got acquired by Samsung SmartThings in April 2016.}
        \xpbul{Implemented asynchronous WebRTC signaling server in Python Tornado, with focus on scalability and failover.}
        \xpbul{Led embedded camera effort, developed WebRTC client for ARM Linux.}
        \xpbul{Developed cloud-based media processors using GStreamer.}
}}

\xprow
{\xpcell{2014}{}{}{
        \xptitlelong{Alphaworks, a Betaworks company}{Product Engineer Consultant}
        \xpbul{Developed MVP for alphaworks.net (crowd investing platform).}
        \xpbul{Led development of admin tools to enable efficient deal management.}
}}
{\xpcell{2012}{--}{2014}{
        \xptitlelong{Rhizome at the New Museum}{Senior Developer}
        \xpbul{Developed and maintained arts non-profit website rhizome.org.}
        \xpbul{Co-managed the ArtBase (award-winning collection of digital art), and served as an advocate for digital art and digital preservation.}
}}

%\xprow
%{\xpcell{2011}{--}{2012}{
%        \xptitle{Sanders New Media}{Software Engineer}
%        \xpbul{Developed applications for web and mobile.}
%        \xpbul{Projects: iOS games, flash sales site, social networking app, digital comic and more.}
%}}
%{\xpcell{}{}{}{
%}}
%{\xpcell{Summer}{}{2008}{
%        \xptitle{Computer History Museum}{Volunteer}
%        \xpbul{Assisted with packaging and cataloging of com\-puter-related artifacts.}
%}}

%\xprow
%{\xpcell{2007}{--}{2010}{
%        \xptitle{Orchestral Colour Records}{Co-founder}
%        \xpbul{Co-founded independent record label representing artists from genres including Electronic, Pop and Hip-Hop.}
%        %\xpbul{Creative direction in advertising and promotional materials for web, TV and print.}
%}}

\vfil \break

\title{Education}
\bulpoint{Columbia College Chicago - BA in Photography, minor in Web Development, 2006 – 2010 cum laude.}

\title{Languages and Technologies}
\bulpoint{Python, JavaScript, AWK, Bash, C, jQuery, HTML/CSS}
\bulpoint{AWS, GNU/Linux, macOS, Git, Docker, Terraform, MariaDB, GStreamer, WebRTC, Nginx, \TeX{}}
\bulpoint{Familiar with: C++, GLib, Java, RTSP, Make}

\title{Accolades}
\bulpoint{Perspective Gallery - Work selected for LENSE 2011 juried exhibition}
\bulpoint{Poet and Didn't Know it Award - The American Computer Experience 1998}

\title{Speaking Engagements}
\bulpoint{''Net Art Anatomy'' workshop, Mozilla Festival, London, October 2014}

\title{Shared Exhibitions}
\bulpoint{2011 - Perspective Gallery, LENSE 2011.}
\bulpoint{2011 - Photography B.A. + B.F.A. Manifest Exhibit.}

\title{Collections}
\bulpoint{Columbia College Chicago Permanent Collection}

\title{Publications}
\bulpoint{There and Back (Again): Homebrew Computer Club at 38. Rhizome Journal. December 16, 2013.}
\bulpoint{http://rhizome.org/editorial/2013/dec/16/there-and-back-again-homebrew-computer-club-38/}

\bye
